Paper figures

### 2019-06-21 voltagebudget/analysis/paper_figures_redraft.Rmd
Removed redundant panel from trade-off fig

# The trade off
```{r, fig.width=2, fig.height=5}
# By freq
fig2 %>% 
  filter(V_osc/V_comp <= 5) %>%
  ggplot(aes(x=V_osc*mV, errors_pop*ms, group=freq, color=freq)) +
  geom_line(size=.5, alpha=0.8) +
  scale_colour_continuous("Freq.", low="lightsalmon1", high="orange4") +
  xlab(expression(paste(V[o], " (mV)"))) +
  ylab("Error (ms)") +
  theme_classic() +
  theme(legend.position="none") -> p1
fig2 %>% 
  filter(V_osc/V_comp <= 5) %>%
  ggplot(aes(x=V_osc*mV, variances_pop*ms, group=freq, color=freq)) +
  geom_line(size=.5, alpha=0.8) +
  scale_colour_continuous("Freq.", low="lightsalmon1", high="orange4") +
  xlab(expression(paste(V[o], " (mV)"))) +
  ylab("Variance (ms)") +
  theme_classic() +
  theme(
    legend.position=c(0.45, 1.5),
    legend.direction="horizontal",    
    legend.key.size = unit(.5, "cm"),
    legend.key.height=unit(0.3,"cm"),
    legend.title = element_text(size=8),
    legend.text = element_text(size=8),
    legend.background = element_rect(colour ="black")) -> p2

# Norm
fig2 %>% 
  filter(V_osc/V_comp <= 5) %>%
  group_by(freq, N) %>%
  mutate(errors_pop = normalize(errors_pop)) %>%
  mutate(variances_pop = normalize(variances_pop)) %>%
  ggplot(aes(x=V_osc/V_comp, errors_pop, group=freq)) +
  geom_line(size=.5, alpha=0.5) +
  geom_hline(yintercept = 0.5, alpha=1, color="grey", linetype="dashed") +
  annotate("text", x = 4, y = 0.65, label = expression(paste("E"[50]))) +
  xlab(expression(V[o]/V[c])) +
  ylab("Norm. error") +
  theme_classic() -> p3
fig2 %>% 
  filter(V_osc/V_comp <= 5) %>%
  group_by(freq, N) %>%
  mutate(errors_pop = normalize(errors_pop)) %>%
  mutate(variances_pop = normalize(variances_pop)) %>%
  ggplot(aes(x=V_osc/V_comp, variances_pop, group=freq)) +
  geom_line(size=.5, alpha=0.5) +
  xlab(expression(V[o]/V[c])) +
  ylab("Norm. variance") +
  theme_classic() -> p4

@@

tmp %>% 
  filter(V_osc/V_comp <= 5) %>%
  group_by(freq, N) %>%
  mutate(errors_pop = normalize(errors_pop)) %>%
  mutate(variances_pop = normalize(variances_pop)) %>%
  ggplot(aes(x=variances_pop, errors_pop, group=freq, color=state)) +
  geom_point(size=.8, alpha=0.8) +
  xlab("Norm. variance") +
  ylab("Norm. error") +
  scale_color_manual("State", values=c("darkslategray3", "darkslategray")) +
  theme_classic() +
  theme(legend.background = element_rect(colour ="black")) -> p7

print(summary(fig2_ratios$ratio))
fig2_ratios %>% 
  ggplot(aes(x=freq, y=ratio)) +
  geom_point(color="darkslategray3", size=1.6) +
  xlab("Freq. (Hz)") +
  geom_hline(yintercept = mean(fig2_ratios$ratio), alpha=0.8, color="darkslategray3", linetype="solid") +
  ylab(expression(paste(V[o]/V[c], " at E"[50]))) +
  theme_classic() +
  ylim(0, 1) -> p8

plot_grid <- rbind(
  c(NA, NA, NA, NA),
  c(NA, NA, NA, NA),
  c(1, 1, 2, 2), 
  c(1, 1, 2, 2),
  c(1, 1, 2, 2),
  c(1, 1, 2, 2),
  c(NA, NA, NA, NA),
  c(3, 3, 4, 4),
  c(3, 3, 4, 4),
  c(3, 3, 4, 4),
  c(3, 3, 4, 4),
  c(NA, NA, NA, NA),
  c(8, 8, 8, NA),
  c(8, 8, 8, NA),
  c(8, 8, 8, NA),
  c(8, 8, 8, NA),
  c(NA, NA, NA, NA),
  c(5, 5, 6, 6),
  c(5, 5, 6, 6),
  c(5, 5, 6, 6),
  c(5, 5, 6, 6),
  c(NA, NA, NA, NA),
  c(7, 7, 7, 7),
  c(7, 7, 7, 7),
  c(7, 7, 7, 7),
  c(7, 7, 7, 7),
  c(7, 7, 7, 7),
  c(7, 7, 7, 7),
  c(7, 7, 7, 7))

grid.arrange(p1, p2, p3, p4, p5, p6, p7, p8, layout_matrix=plot_grid)
```

>>>>

# The trade off
```{r, fig.width=2.2, fig.height=4}
# By freq
fig2 %>% 
  filter(V_osc/V_comp <= 5) %>%
  ggplot(aes(x=V_osc*mV, errors_pop*ms, group=freq, color=freq)) +
  geom_line(size=.5, alpha=0.8) +
  scale_colour_continuous("Freq.", low="lightsalmon1", high="orange4") +
  xlab(expression(paste(V[o], " (mV)"))) +
  ylab("Error (ms)") +
  theme_classic() +
  theme(legend.position="none") -> p1
fig2 %>% 
  filter(V_osc/V_comp <= 5) %>%
  ggplot(aes(x=V_osc*mV, variances_pop*ms, group=freq, color=freq)) +
  geom_line(size=.5, alpha=0.8) +
  scale_colour_continuous("Freq.", low="lightsalmon1", high="orange4") +
  xlab(expression(paste(V[o], " (mV)"))) +
  ylab("Variance (ms)") +
  theme_classic() +
  theme(
    legend.position=c(0.45, 1.5),
    legend.direction="horizontal",    
    legend.key.size = unit(.5, "cm"),
    legend.key.height=unit(0.3,"cm"),
    legend.title = element_text(size=8),
    legend.text = element_text(size=8),
    legend.background = element_rect(colour ="black")) -> p2

# Norm
fig2 %>% 
  filter(V_osc/V_comp <= 5) %>%
  group_by(freq, N) %>%
  mutate(errors_pop = normalize(errors_pop)) %>%
  mutate(variances_pop = normalize(variances_pop)) %>%
  ggplot(aes(x=V_osc/V_comp, errors_pop, group=freq)) +
  geom_line(size=.5, alpha=0.5) +
  geom_hline(yintercept = 0.5, alpha=1, color="grey", linetype="dashed") +
  annotate("text", x = 4, y = 0.65, label = expression(paste("E"[50]))) +
  xlab(expression(V[o]/V[c])) +
  ylab("Norm. error") +
  theme_classic() -> p3

print(summary(fig2_ratios$ratio))
fig2_ratios %>% 
  ggplot(aes(x=freq, y=ratio)) +
  geom_point(color="darkslategray3", size=1.6) +
  xlab("Freq. (Hz)") +
  geom_hline(yintercept = mean(fig2_ratios$ratio), alpha=0.8, color="darkslategray3", linetype="solid") +
  ylab(expression(paste(V[o]/V[c], " at E"[50]))) +
  theme_classic() +
  ylim(0, 1) -> p4

# fig2 %>% 
#   filter(V_osc/V_comp <= 5) %>%
#   group_by(freq, N) %>%
#   mutate(errors_pop = normalize(errors_pop)) %>%
#   mutate(variances_pop = normalize(variances_pop)) %>%
#   ggplot(aes(x=V_osc/V_comp, variances_pop, group=freq)) +
#   geom_line(size=.5, alpha=0.5) +
#   xlab(expression(V[o]/V[c])) +
#   ylab("Norm. variance") +
#   theme_classic() -> p4

@@

tmp %>% 
  filter(V_osc/V_comp <= 5) %>%
  group_by(freq, N) %>%
  mutate(errors_pop = normalize(errors_pop)) %>%
  mutate(variances_pop = normalize(variances_pop)) %>%
  ggplot(aes(x=variances_pop, errors_pop, group=freq, color=state)) +
  geom_point(size=1.2, alpha=0.8) +
  xlab("Norm. variance") +
  ylab("Norm. error") +
  scale_color_manual("State", values=c("darkslategray3", "darkslategray")) +
  theme_classic() +
  theme(legend.background = element_rect(colour ="black")) -> p7

plot_grid <- rbind(
  c(NA, NA, NA, NA),
  c(NA, NA, NA, NA),
  c(1, 1, 2, 2), 
  c(1, 1, 2, 2),
  c(1, 1, 2, 2),
  c(1, 1, 2, 2),
  c(NA, NA, NA, NA),
  c(3, 3, 4, 4),
  c(3, 3, 4, 4),
  c(3, 3, 4, 4),
  c(3, 3, 4, 4),
  c(NA, NA, NA, NA),
  c(5, 5, 6, 6),
  c(5, 5, 6, 6),
  c(5, 5, 6, 6),
  c(5, 5, 6, 6),
  c(NA, NA, NA, NA),
  c(7, 7, 7, 7),
  c(7, 7, 7, 7),
  c(7, 7, 7, 7),
  c(7, 7, 7, 7),
  c(7, 7, 7, 7),
  c(7, 7, 7, 7),
  c(7, 7, 7, 7))

grid.arrange(p1, p2, p3, p4, p5, p6, p7, layout_matrix=plot_grid)
```
